### 2019-05-22 reviews/response.md

We thank the reviewers for their detailed and insightful feedback.

We have added three new implementations to Task Bench: Dask,
MPI+OpenMP and MPI+CUDA. Results are included in the evaluation
section.

One of the salient features of Task Bench is that it permits the
implementation of a benchmark with M configurations and N systems with
an amount of effort that is O(M+N) rather than O(MN). We have updated
the introduction to reflect this.

Any measure of efficiency can be used with METG. For example, a
mesh-based application could use mesh cells processed per second (as a
percentage of the highest throughput achieved with any problem
size). We use peak performance with Task Bench as it gives us a
straightforward measure that provides assurance that all
implementations are configured correctly.

### 2019-05-22 4_implementation.tex
Add more information on implementations.

Our MPI~\cite{MPI} implementation of Task Bench represents the common
case of point-to-point communication with distinct computation and
communication phases. We experimented with a variety of implementation
strategies and found the best performing to be using
\lstinline[language=C++]{MPI_Isend} and
\lstinline[language=C++]{MPI_Irecv} to implement the communication
phase, posting receives before sends. Each task dependency maps to one
send/receive pair in MPI.

@@

% FIXME: TODO

>>>>

Our MPI~\cite{MPI} implementation of Task Bench represents the common
case of point-to-point communication with distinct computation and
communication phases. We experimented with a variety of implementation
strategies and found the best performing to be using
\lstinline[language=C++]{MPI_Isend} and
\lstinline[language=C++]{MPI_Irecv} to implement the communication
phase, posting receives before sends. Each task dependency maps to one
send/receive pair in MPI. We also provide a bulk synchronous
implementation which enforces the boundary between communication and
computation with \lstinline[language=C++]{MPI_Barrier}.

@@

We provide two MPI+X implementations of Task Bench to evaluate the
performance of hybrid programming models. Our MPI+OpenMP
implementation uses forall-style parallel loops to execute tasks,
interleaved with MPI point-to-point communication as above. Our
MPI+CUDA implementation follows an offload model where data is copied
to and from the GPU on every timestep.
